---
title: "Syllabus Test"
author: "Dr K"
date: "December 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Statement

Create a document that shows your computation of the score you would get in the course if  

1. the total score you got on all ten qiuzzes was 783 points - the top student on quizzes was 987.   
What is your normalized quiz score?  
```{r}
(Nquiz=783/987)
```

2. your score in the swirl/datacamp courses category was 912   top score was 1473: you got 8 badges.   
What is your normalized course score?   
```{r}
(Ncourse=912/1473)
```

3. your workshop category score was 619  top score was 812  What is your normalized workshop score?   
```{r}
(Nworkshop=619/812)
```

4. your DA&DAR score was 412 top score 703  What is your normalized DA&DAR score ?  
```{r}
(NDAR=412/703)
```

5. your grade on final was 82 top score was 100  

```{r}
(Nfinal=82/100)
```

## Overall score

```{r}
(score=20*Nquiz + 20*Ncourse + 15*Nworkshop + 20*NDAR + 25*Nfinal)
```

## Final Grade C